Make any stupid plot you want

### 2020-12-01 draft/sections/math.tex
unpacking U

\begin{equation}
    A: \Gamma(E) \rightarrow \Gamma(H)
    \lab{eq:artist}
\end{equation}

\begin{enumerate}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $K$ is a triangulizable space encoding the connectivity of the observations in the data. 
\item $H$ is a fiber bundle over $S$ representing visual space
\item $S$ is a simplacial complex of triangles encoding the connectivity of the visualization of $\Gamma(E)$
\end{enumerate}

When E is a trivial fiber bundle $E = F \times K$, it can be assumed that all $F_{k}$ for $k \in K$ are equal. Fiber bundles are product spaces of toplological spaces, which are a set of points with a set of neighborhoods for each point\cite{some topology text book, really wikipedia}.

\subsection{Data Model}
\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}

    %% simpler still replace w/ timeseries of temp, 1D fiber -> inspired by butler 1989 FIgG 1
\end{figure}

%%% preface w/ we care about topology & types. 
We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}.

A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

@@

The space of all $\sigma$ is $\Gamma$  (Pull this back into more specific about fig, the general is making this more confusing.)
%% locally trivial - for every point in K there exists an open set neighborhood $U$ such that if you restrict E to that point, then  \iota*E = F\times U [maybe do mobius strip diagram here? U is subsection of the ring, part where it's not twisted. there exists a triangulation & a way to do so is simplicies

\subsubsection{Base Space $K$}
\begin{figure}
    \includegraphics{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}
    \includegraphics{figures/sections/math/temp_2k.png}
\end{figure}
%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary
%% k is a topological space ....equation soup

\subsubsection{Fiber Space $F$}
\begin{figure}
    \includegraphics{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}
    \includegraphics{figures/sections/math/temp_3f.png}
\end{figures}
%%% might 
The fibers $F$ are a topological space embedded in $E$ on which lie the set of all possible values. For example, if $F$ is the interval $[0, 1]$, then $g(k)$ from equation~\ref{eq:sigma} returns a single measurement $x$ in the interval $F$:
\begin{equation}
    \label{eg:goff}
    g(k) = x, \text(where} 0\leq x \leq 1
\end{equation}

The fiber in figure~\ref{fig:temp} is the space of possible temperature values in $\circ$ celsius, ranging from [start, end], similar to the interval $F$ in equation~\ref{eg:goff}. F can be any number of dimensions, for example in figure~\ref{fig:temp_time} time is encoded as a second dimension. Given:
\begin{enumerate}
\item interval of all possible temperarture values $\[T_{min}, T_{max}\]$ 
\item interval of all possible  time values $\[t_{min}, t_{max}\]$
\end{enumerate}

then $F$ is the cross product $F= $\[T_{min}, T_{max}\]$  \times

$g(k) = (temp, time)$.  
\begin{equation}
\end{equation}

As an alternative to listing the intervals or discrete values

@@

Tau is fully flexible and can do whatever; knows about fiber & neighborhood of fiber. Can in theory approximate hatching/dashing/etc can be approximated w/ functions and neighborhood of k. 
\subsubsection{Visual Idioms: Equivalance class of artists}
Two artists are equivalent when given data containers $\Gamma(E)$ of the same type, they output the same type of prerender $\Gamma(S)$:
\begin{equation}
    \begin{tikzcd}
        A_{\tau_2}: \arrow[d, shift right=2] & \Gamma(E) \arrow[r] & \Gamma(H) &                                                \\
        A_{\tau_1}: \arrow[u, shift right]   & \Gamma(E) \arrow[r] & \Gamma(H) 
    \end{tikzcd}
\end{equation}

>>>>

\begin{equation}
    A: \Gamma(E) \rightarrow \Gamma(H)
    \label{eq:artist}
\end{equation}

\begin{itemize}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $K$ is a triangulizable space encoding the connectivity of the observations in the data. 
\item $H$ is a fiber bundle over $S$ representing visual space
\item $S$ is a simplacial complex of triangles encoding the connectivity of the visualization of $\Gamma(E)$
\end{itemize}

When $E$ is a trivial fiber bundle $E = F \times K$, it can be assumed that all $F_{k}$ for $k \in K$ are equal. Fiber bundles are product spaces of toplological spaces, which are a set of points with a set of neighborhoods for each point\cite{some topology text book, really wikipedia}. We will be discussing total spaces $E$ that are locally trivial, meaning that for every point in K there exists an open set neighborhood $U$ such that if you restrict $E$ to that point, then  $\iota*E = F\times U$. [there's a missing sentance here...]

\subsection{Data Model}
\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
    %% simpler still replace w/ timeseries of temp, 1D fiber -> inspired by butler 1989 FIgG 1
\end{figure}

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}. A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$.

@@

The space of all $\sigma$ is $\Gamma$  (Pull this back into more specific about fig, the general is making this more confusing.)

\subsubsection{Base Space $K$}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}
%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary
%% k is a topological space ....equation soup

\subsubsection{Fiber Space $F$}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2f.png}
    \label{fig:}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_3f.png}
\end{figure}
%%% might 
The fibers $F$ are a topological space embedded in $E$ on which lie the set of all possible values. For example, if $F$ is the interval $[0, 1]$, then $g(k)$ from equation~\ref{eq:sigma} returns a single measurement $x$ in the interval $F$:
\begin{equation}
    \label{eg:goff}
    g(k) = x, \text{ where } 0\leq x \leq 1
\end{equation}

The fiber in figure~\ref{fig:temp} is the space of possible temperature values in $\circ$ celsius, ranging from [start, end], similar to the interval $F$ in equation~\ref{eg:goff}. F can be any number of dimensions, for example in figure~\ref{fig:temp_time} time is encoded as a second dimension. Given:
\begin{itemize}
\item interval of all possible temperature values $[T_{min}, T_{max}]$ 
\item interval of all possible  time values $[t_{min}, t_{max}]$
\end{itemize}

then $F$ is the cross product $F= [T_{min}, T_{max}] \times [t_{min}, t_{max}]$, and $g(k)$ listed in equation~\ref{eq:sigma} is:

\begin{equation}
g(k) = (x_0, x_1) \text{ where } x_0 \in [T_{min}, T_{max}], x_1 \in [t_{min}, t_{max}]
\end{equation}

Given $F = X_{0} \times X_{1} \times \ldots \times X_{n}$, where $X_{0}, X_{1}, \ldots X_{n}$ are measurement spaces (e.g. ints, floats, colors): 
\begin{equation}
g(k) = (x_0, x_1, \ldots x_n) \text{ where } x_0 \in X_0, x_1 \in X_1, \ldots x_n \in X_n
\end{equation}

The measurement spaces $X$ are each variables and have the properties of measurement scales, such as Steven's nominal, ordinal, interval, and ratio \cite{stevensTheoryScalesMeasurement1946}. 
Spivak provides a formal way of attaching a name to each $X \in F$ and mapping from the value back to the variable type by formulating $E$ in terms of databases \cite{spivakSIMPLICIALDATABASES}. He defines a total space $U$, analogous to $E$, that is the disjoint union of all possible elements of all possible types

For example, the interval $[T_{min}, T_{max}]$ is a restriction on $\mathbb{R}$ that is part of the definition of a type named $\mathrm{Temperature}$ and  $[t_{min}, t_{max}]$ is a restriction on $\mathbb{R}$ that is part of a definition of a type named $\mathrm{Time}$. As in the case of $E$ embedding the $F$ on which these values live, $U$ contains all pairs of all values of these types $U \coloneqq (\mathrm{Temperature}, \mathrm{Time})$. Spivak defines U as being over the space of $\mathrm{DT}$, which is the space of data types $\mathrm{DT} = \{\mathrm{Temperature}, \mathrm{Time}}$.

@@

Tau is fully flexible and can do whatever; knows about fiber \& neighborhood of fiber. Can in theory approximate hatching/dashing/etc can be approximated w/ functions and neighborhood of k. 
\subsubsection{Visual Idioms: Equivalance class of artists}
Two artists are equivalent when given data containers $\Gamma(E)$ of the same type, they output the same type of prerender $\Gamma(S)$:
\begin{equation}
    \begin{tikzcd}
        A_{\tau_2}: \arrow[d, shift right=2] & \Gamma(E) \arrow[r] & \Gamma(H) &                                                \\
        A_{\tau_1}: \arrow[u, shift right]   & \Gamma(E) \arrow[r] & \Gamma(H) 
    \end{tikzcd}
\end{equation}
